---
title: "Example Roundup"
author: "Michael Griebe"
date: "October 20, 2016"
output: 
  html_document: 
    keep_md: yes
---
```{r setup, echo=FALSE,message=FALSE,results='hide',warning=FALSE}
require(data.table)
require(ggplot2)
require(RColorBrewer)
require(knitr)
require(zoo)
require(mclust)
require(DT)
require(ggthemes)

#Must Define next_week before sourcing "weeklyRoundup.R"
next_week=5
source("../R/WeeklyRoundup.R")
####  Combine Standard Scoring and PPR scoring into single table. 
# Standard Scoring Projections Table
# LT4 stands for league type 4, which is a standard scoring league.
# load the file -it dumps projectedPoints into the workspace.
load(file=paste0("../data/week",next_week,"LT4","projections.RData"))
# rename (by reference since its a data table) projected points.
StandardWP<-projectedPoints
# remove the old reference.
rm(projectedPoints)
# add the column "leagueType" and make every entry "Standard".
StandardWP[,leagueType:="Standard"]

## PPR Scoring Table
load(file=paste0("../data/week",next_week,"LT8","projections.RData"))
PPRWP <-projectedPoints
rm(projectedPoints)
PPRWP[,leagueType:="PPR"]

## .5 PPR Scoring Table
load(file=paste0("../data/week",next_week,"LT8","projections.RData"))
HPPRWP <- projectedPoints
HPPRWP[,leagueType:="HPPR"]

# create one table from the three tables (WP stands for Weekly Projections)
WP<-rbindlist(list(StandardWP,PPRWP,HPPRWP))

# Some sources were not removing players on a bye week.  We did not catch this until the first bye week.
# So, if you run this line of code with week 1-5 data, it will not work -just omit it.

if(next_week>4) {WP<-WP[next_week!=byeweek]}

# Generate sumary table by player.  The "model" variable holds the Hodges-Lehmann estimator.
Models<- WP[,list(model=list(h.l(points)),
                  nAnalysts=length(unique(analystId)),
                  mean=mean(points,na.rm=TRUE),
                  floor=quantile(points,.1),
                  ceiling=quantile(points,.9)),
            by=list(player,team,position,leagueType,playerId)]

# Throw out players with less than 4 projections -in early weeks, due to the move of the Rams, we did not get
# the full compliment of sources, hence we include the rams even if it does not meet the 3 or more analyst threshold.

Models<-Models[nAnalysts>=3|player=="Rams"]

# Extract the pm, pm_l, and pm_h from each player's model.
Models[,c("pm","pm_l","pm_h"):=list(vapply(model,function(x){x$estimate},double(1)),
                                    vapply(model,function(x){x$conf.int[1]},double(1)),
                                    vapply(model,function(x){x$conf.int[2]},double(1)))]

# Don't allow the lower confidence bound to be negative.  This is only a problem if there are few
# analytsts.

Models[pm_l<0,pm_l:=0]

#Add Rank by pm.
Models[order(-pm),rank:=1:.N,by=list(position,leagueType)]

#Reduce to top 60 in each position.
Models<-Models[rank<60]

# Cluster based on pseudomeans - to give the charts some color.  There are other possible interesting
# ways to cluster.  For instance, one could do a multi-dimensional cluster on analyst projections.
# One dimension would be NFL projections, the next, CBS, etc.
Models[,tier:=Mclust(-pm, G=6)$classification,by=list(leagueType,position)]

# There are other ways to calculate the upside and downside.
Models[,upside:=ceiling-pm]
Models[,downside:=pm-floor]
# This is easiest to explain, but it may not conform with the standard notion of upside.
# One alternative that I have tossed around is
# Upside = ceiling + floor - 2*pm
# Downside = 2*pm - ceiling - floor
# This definition essentially captures how skewed the distribution is.
# Arguably, if the projections are all over the place symetrically, then you don't have upside or downside, you have
# variation.  If the projections are skewed to the right, then you have upside.  If they are skewed left, then you
# have downside.

# Extract discussion about articles.
writers<-unique(WP$analystName)

# Get the injury status -I have not been saving this table weekly, so I only have the most recent version.
load(file="../data/injuryStatus-2016-10-20.RData")

# For our articles, we extract the update date from the database of projections.
# Here, we just use today for demonstration purposes.
UpdateDate<-Sys.Date()

#Add Injury Status to the Models Table
Models<-merge(Models,injuryStatus[,list(playerId,injuryStatus)],by="playerId",all.x = TRUE)

Models[is.na(injuryStatus),injuryStatus:="Healthy"]
unique(Models$injuryStatus)
#Abbreviate injury statuss.
injAbrv=list(Questionable="Q",Out="Out",Doubtful="D",IR="IR",`Ir-pup`="IR",`Ir-nfi`="IR",Healthy="",
             Suspended="Susp")
#Warning is not enough here.  Need a stop.  Recycling is BAD.
if(nrow(Models)!=length(unlist(injAbrv[Models$injuryStatus]))){stop("Something is wrong with the injury list.")}

Models[,Status:=unlist(injAbrv[injuryStatus])]
Models[,injuryStatus:=NULL]

#If there are any players to exclude from commentary, put them here.
#exclude=c("Jordy Nelson","Trent Richardson","Kelvin Benjamin")
exclude=NULL
```

Welcome to week `r next_week`. The graphs below summarize the projections from a variety of sources.  This week&rsquo;s summary includes projections from: `r p_and(writers)`.  The data for this article was collected on `r format(as.Date(UpdateDate), format="%D")`. For more details on WR gold mining and how to interpret the graphs above, see [Chad&rsquo;s post explaining gold mining](http://fantasyfootballanalytics.net/2014/11/gold-mining-explained.html).


## Projection Table
```{r datatable,echo=FALSE,message=FALSE,warning=FALSE}
datatable(Models[order(leagueType,mean,decreasing = T),
                     list(Player=player,
                          Status=as.factor(Status),
                          Team=as.factor(team),
                          Position=as.factor(position),
                          Scoring=as.factor(leagueType),
                          Mean=round(mean,1),
                          Floor=round(floor,1),
                          Ceiling=round(ceiling),
                           `Number of Analysts Included`=nAnalysts)],
              rownames=F,filter='top',options=list(lengthChange=F,pageLength=15))
```


## Projection Graphs Standard Leagues  {.tabset .tabset-pills}
### RB
#### Standard Scoring League Running Backs

From the graph below notice that:
  
- `r bullet1("RB","Standard")`
- `r bullet2("RB","Standard")`
- `r bullet3("RB","Standard")`

<center> 
```{r Standard_RB,echo=FALSE,message=FALSE,warning=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models,"RB","Standard",60,next_week)
```
</center>
  
  
### WR
#### Standard Scoring League Wide Receiver 
  
From the graph below notice that:

- `r bullet1("WR","Standard")`
- `r bullet2("WR","Standard")`
- `r bullet3("WR","Standard")`

<center> 
```{r Standard_WR,message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models, "WR","Standard",60,next_week)
```
</center>
  
### QB
#### Standard Scoring League Quarterback
  
From the graph below notice that:
  
- `r bullet1("QB","Standard")`
- `r bullet2("QB","Standard")`
- `r bullet3("QB","Standard")`


<div>
<center>
```{r Standard_QB, message=FALSE,warning=FALSE,echo=FALSE,fig.height=8,fig.width=9,dpi=100}
roundupGraph(Models,"QB","Standard",60,next_week)
```
</center>
</div>
  
### TE
#### Standard Scoring League Tight-End
  
From the graph below notice that:
  
- `r bullet1("TE","Standard")`
- `r bullet2("TE","Standard")`
- `r bullet3("TE","Standard")`


<div>
<center>
```{r Standard_TE,message=FALSE,warning=FALSE,echo=FALSE,fig.height=8,fig.width=9,dpi=100}
roundupGraph(Models,"TE","Standard",60,next_week)
```
</center>
</div>
  
  
## Projection Graphs Point-per-Reception Leagues  {.tabset .tabset-pills} 
### RB
#### Point-per-Reception League Running Back Roundup
  
  From the graph below notice that:
  
- `r bullet1("RB","PPR")`
- `r bullet2("RB","PPR")`
- `r bullet3("RB","PPR")`


<center> 
```{r PPR_RB,message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models, "RB","PPR",60,next_week)
```

</center>
  
  
### WR
#### Point-per-Reception League Wide Receiver
  
From the graph below notice that:
  
- `r bullet1("WR","PPR")`
- `r bullet2("WR","PPR")`
- `r bullet3("WR","PPR")`


<center> 
```{r PPR_WR, message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models, "WR","PPR",60,next_week)
```
</center>
  
  
### QB
#### Point-per-Reception League Quarterback
  
From the graph below notice that:
  
- `r bullet1("QB","PPR")`
- `r bullet2("QB","PPR")`
- `r bullet3("QB","PPR")`

<div>
<center>
```{r PPR_QB, message=FALSE,warning=FALSE,echo=FALSE,fig.height=8,fig.width=9,dpi=100}
roundupGraph(Models,"QB","PPR",60,next_week)
```
</center>
</div>
  
### TE
#### Point-per-Reception League Tight-End
  
From the graph below notice that:
  
- `r bullet1("TE","PPR")`
- `r bullet2("TE","PPR")`
- `r bullet3("TE","PPR")`

<div>
<center>
```{r PPR_TE,message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models,"TE","PPR",60,next_week)
```
</center>
</div>

## Projection Graphs Half-Point-per-Reception Leagues  {.tabset .tabset-pills} 
### RB
#### Half-Point-per-Reception League Running Back Roundup
  
  From the graph below notice that:
  
- `r bullet1("RB","PPR")`
- `r bullet2("RB","PPR")`
- `r bullet3("RB","PPR")`


<center> 
```{r HPPR_RB,message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models, "RB","HPPR",60,next_week)
```

</center>
  
  
### WR
#### Half-Point-per-Reception League Wide Receiver
  
From the graph below notice that:
  
- `r bullet1("WR","PPR")`
- `r bullet2("WR","PPR")`
- `r bullet3("WR","PPR")`


<center> 
```{r HPPR_WR, message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models, "WR","HPPR",60,next_week)
```
</center>
  
  
### QB
#### Half-Point-per-Reception League Quarterback
  
From the graph below notice that:
  
- `r bullet1("QB","PPR")`
- `r bullet2("QB","PPR")`
- `r bullet3("QB","PPR")`

<div>
<center>
```{r HPPR_QB, message=FALSE,warning=FALSE,echo=FALSE,fig.height=8,fig.width=9,dpi=100}
roundupGraph(Models,"QB","HPPR",60,next_week)
```
</center>
</div>
  
### TE
#### Half-Point-per-Reception League Tight-End
  
From the graph below notice that:
  
- `r bullet1("TE","PPR")`
- `r bullet2("TE","PPR")`
- `r bullet3("TE","PPR")`

<div>
<center>
```{r HPPR_TE,message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models,"TE","HPPR",60,next_week)
```
</center>
</div>


## Projection Graphs Defense/Special Teams and Kickers  {.tabset .tabset-pills}
### DST
#### Standard Scoring DST

From the graph below notice that:
  
- `r bullet1("DST","Standard")`
- `r bullet2("DST","Standard")`
- `r bullet3("DST","Standard")`

<center> 
```{r DST, message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models,"DST","Standard",30,next_week)
```
</center>

### K
#### Standard Scoring K

From the graph below notice that:
  
- `r bullet1("K","Standard")`
- `r bullet2("K","Standard")`
- `r bullet3("K","Standard")`

<center> 
```{r K, message=FALSE,warning=FALSE,echo=FALSE,fig.height=10,fig.width=9,dpi=100}
roundupGraph(Models,"K","Standard",30,next_week)
```
</center>
  
