---
title: "Gold Mining"
author: "Fantasy Football Analytics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, echo=FALSE,message=FALSE,results='hide',warning=FALSE}
require(data.table)
require(ggplot2)
require(RColorBrewer)
require(knitr)
require(seqinr)
require(mclust)
require(ggvis)
source("../../R Scripts/Functions/MRGFunctions.R")
load("ffa_wr.RData")
ffa<-ffa[min_rank<36]

sstat <- function(x){
  return(list("Lowest Projection"=min(x),"Highest Projection"=max(x),
              "Mean Projection" = mean(x),"Standard Deviation"=sd(x), "Median Projection"=median(x)))
         }
h.l <- function(x){tryCatch({
  wilcox.test(x,na.action="na.exclude",conf.int=TRUE)},
  error=function(e){return(list(estimate=median(x),conf.int=c(median(x)-sd(x),median(x)+sd(x))))})
}

htests<-ffa[,list(ppr_mean=mean(ppr_fpts),std_mean=mean(std_fpts),
                  ppr_min=min(ppr_fpts),ppr_max=max(ppr_fpts),
                  ppr_ave_rank=mean(ppr_rank), std_ave_rank=mean(std_rank),
                  ppr_h.l=list(h.l(ppr_fpts)),std_h.l=list(h.l(std_fpts))),by=name]
htests[,c("ppr_pm","ppr_pm_l","ppr_pm_h"):=list(vapply(ppr_h.l,function(x){x$estimate},double(1)),
                                    vapply(ppr_h.l,function(x){x$conf.int[1]},double(1)),
                                    vapply(ppr_h.l,function(x){x$conf.int[2]},double(1)))]
htests[,c("std_pm","std_pm_l","std_pm_h"):=list(vapply(std_h.l,function(x){x$estimate},double(1)),
                                    vapply(std_h.l,function(x){x$conf.int[1]},double(1)),
                                    vapply(std_h.l,function(x){x$conf.int[2]},double(1)))]

#clustering based on means.
htests[,c("ppr_tier","std_tier"):=list(Mclust(ppr_pm, G=7)$classification,Mclust(std_pm,G=7)$classification)]

htests[,c("ppr_h.l","std_h.l"):=NULL]
htests[order(-ppr_pm),ppr_rank:=1:.N]
htests[order(-std_pm),std_rank:=1:.N]
ffa[,c("std_ave_fpts","ppr_ave_fpts"):=list(mean(std_fpts),mean(ppr_fpts)),by=name]
premium<-ffa[,list(name,writer,premium=std_fpts-std_ave_fpts)]
wpremium<-BreakBuild(premium,BCol = "writer",IDCols = "name",ValCols = "premium")
writers<-list(ffs="Fantasy Football Sharks",jamey_eisenberg="CBS's Jamey Eisenberg", dave_richard="CBS's Dave Richard",espn="ESPN",pp="Picking Pros",yahoo="Yahoo Sports",fx="Fox Sports",fft="Fantasy Football Today")
wpremium

htests[,std_upside:=std_pm_h-std_pm]
htests[,std_downside:=std_pm-std_pm_l]

htests[,ppr_upside:=ppr_pm_h-ppr_pm]
htests[,ppr_downside:=ppr_pm-ppr_pm_l]

p_and<- function(x) {
  paste(paste(x[1:(length(x)-1)],collapse=", "), "and", x[length(x)])
}

```

The graph below summarizes the projections from a variety of sources.  This week's summary includes projections from: `r p_and(writers[ffa[,unique(writer)]])`.

## Standard Scoring Leagues
### Week `r next_week` Wide Receivers 

From this graph be sure to notice:

 - `r p_and(htests[order(-std_upside)][1:5][order(std_ave_rank)][,unique(name)])` are the five players with the <b>largest upside</b> (as measured from their (pseudo)medians).  For these players, some projections are placing much higher valuations than others. If you are projected to lose this week by quite a few points and are looking for a risky play that may tip the balance in your favor, these are players to consider.
 - `r p_and(htests[order(std_downside)][1:5][order(std_ave_rank)][,unique(name)])` are the playres with the <b> smallest downside</b>, which suggests that while their median projection might not be great, there is less uncertainty concerning how poorly they may perform.  So, if your are likely to win by a lot and want to reduce your downside risk, these players may deserve extra attention.
 - On the other hand, `r p_and(htests[order(-std_downside)][1:5][order(std_ave_rank)][,unique(name)])`  are the five playres with the <b>largest downside</b> this week.  If you are planning on starting them, it may be prudent to investigate why some projections have such low expectations for these players.
 
<center> 
```{r,echo=FALSE,fig.height=8,fig.width=8}
#graphing
#geom_point(size=3)+
ggplot(htests, aes(x=std_pm, y=std_rank, color=factor(std_tier))) +
  geom_errorbarh(aes(xmin=std_pm_l,xmax=std_pm_h),height=.3)+
  geom_point(size=5,color="white")+
  geom_text(aes(x=std_pm,label=round(std_pm,0)),size=3)+
  geom_text(aes(x=std_pm_h, label=name, hjust=-0.2, angle=(0), size=1))+
  theme(
    plot.background = element_blank()
    ,panel.grid.major.x = element_line(color="grey")
    ,panel.grid.minor.y = element_line(color="grey")
    ,panel.border=element_rect(color="grey",fill=NA)
    ,panel.background = element_blank()
    ,legend.position = "none"
  ) + scale_y_reverse()+
  ylab("Average Rank") + xlab("Median FPTS Projection with Confidence Interval") +
  labs(title = paste("Week ", next_week, " Wide Receiver Projections Roundup", sep="")) +
  coord_cartesian(xlim =c(0,(max(htests$std_pm_h)+10))) 
```
</center>


```{r,echo=FALSE, results='asis', message=FALSE,warning=FALSE}
##kable(ffa[order(std_ave_rank)][,c(sstat(std_fpts),list("Average Rank"=mean(ppr_rank))),
##          by=name][1:30])
```


## PPR Leagues
### Week `r next_week` Wide Receivers 

From this graph be sure to notice:

 - `r p_and(htests[order(-ppr_upside)][1:5][order(ppr_ave_rank)][,unique(name)])` are the five players with the <b>largest upside</b> (as measured from their (pseudo)medians).  For these players, some projections are placing much higher valuations than others. If you are projected to lose this week by quite a few points and are looking for a risky play that may tip the balance in your favor, these are players to consider.
 - `r p_and(htests[order(ppr_downside)][1:5][order(ppr_ave_rank)][,unique(name)])` are the playres with the <b> smallest downside</b>, which suggests that while their median projection might not be great, there is less uncertainty concerning how poorly they may perform.  So, if your are likely to win by a lot and want to reduce your downside risk, these players may deserve extra attention.
 - On the other hand, `r p_and(htests[order(-ppr_downside)][1:5][order(ppr_ave_rank)][,unique(name)])` are the five playres with the <b>largest downside</b> this week.  If you are planning on starting them, it may be prudent to investigate why some projections have such low expectations for these players.

<center> 
```{r,echo=FALSE,fig.height=8, fig.width=8}
#graphing
#geom_point(size=3)+
ggplot(htests, aes(x=ppr_pm, y=ppr_rank, color=factor(ppr_tier))) +
  geom_errorbarh(aes(xmin=ppr_pm_l,xmax=ppr_pm_h),height=.3)+
  geom_point(size=5,color="white")+
  geom_text(aes(x=ppr_pm,label=round(ppr_pm,0)),size=3)+
  geom_text(aes(x=ppr_pm_h, label=name, hjust=-0.2, angle=(0), size=1))+
  theme(
    plot.background = element_blank()
    ,panel.grid.major.x = element_line(color="grey")
    ,panel.grid.minor.y = element_line(color="grey")
    ,panel.border=element_rect(color="grey",fill=NA)
    ,panel.background = element_blank()
    ,legend.position = "none"
  ) + scale_y_reverse()+
  ylab("Average Rank") + xlab("Median FPTS Projection with Confidence Interval") +
  labs(title = paste("Week ", next_week, " Wide Recevier Projections Roundup", sep="")) +
  coord_cartesian(xlim =c(0,(max(htests$ppr_pm_h)+10))) 

```
</center> 


```{r,echo=FALSE, results='asis'}
##kable(ffa[order(ppr_ave_rank)][,c(sstat(ppr_fpts),list("Average Rank"=mean(ppr_rank))),
##          by=name][1:30])
```


