---
title: "Gold Mining"
author: "Fantasy Football Analytics"
date: "Friday, October 31, 2014"
output: html_document
---

```{r, echo=FALSE,message=FALSE,results='hide',warning=FALSE}
require(data.table)
require(ggplot2)
require(RColorBrewer)
require(knitr)
require(seqinr)
require(mclust)
require(ggvis)
source("../../R Scripts/Functions/MRGFunctions.R")
load("ffa_wr.RData")
ffa<-ffa[min_rank<36]

sstat <- function(x){
  return(list("Lowest Projection"=min(x),"Highest Projection"=max(x),
              "Mean Projection" = mean(x),"Standard Deviation"=sd(x), "Median Projection"=median(x)))
         }
h.l <- function(x){tryCatch({
  wilcox.test(x,na.action="na.exclude",conf.int=TRUE)},
  error=function(e){return(list(estimate=median(x),conf.int=c(median(x)-sd(x),median(x)+sd(x))))})
}

htests<-ffa[,list(ppr_mean=mean(ppr_fpts),std_mean=mean(std_fpts),
                  ppr_min=min(ppr_fpts),ppr_max=max(ppr_fpts),
                  ppr_ave_rank=mean(ppr_rank), std_ave_rank=mean(std_rank),
                  ppr_h.l=list(h.l(ppr_fpts)),std_h.l=list(h.l(std_fpts))),by=name]
htests[,c("ppr_pm","ppr_pm_l","ppr_pm_h"):=list(vapply(ppr_h.l,function(x){x$estimate},double(1)),
                                    vapply(ppr_h.l,function(x){x$conf.int[1]},double(1)),
                                    vapply(ppr_h.l,function(x){x$conf.int[2]},double(1)))]
htests[,c("std_pm","std_pm_l","std_pm_h"):=list(vapply(std_h.l,function(x){x$estimate},double(1)),
                                    vapply(std_h.l,function(x){x$conf.int[1]},double(1)),
                                    vapply(std_h.l,function(x){x$conf.int[2]},double(1)))]

#clustering based on means.
htests[,c("ppr_tier","std_tier"):=list(Mclust(ppr_mean, G=7)$classification,Mclust(std_mean,G=7)$classification)]

htests[,c("ppr_h.l","std_h.l"):=NULL]
htests[order(-ppr_pm),ppr_rank:=1:.N]
htests[order(-std_pm),std_rank:=1:.N]
ffa[,c("std_ave_fpts","ppr_ave_fpts"):=list(mean(std_fpts),mean(ppr_fpts)),by=name]
premium<-ffa[,list(name,writer,premium=std_fpts-std_ave_fpts)]
wpremium<-BreakBuild(premium,BCol = "writer",IDCols = "name",ValCols = "premium")
writers<-list(ffs="Fantasy Football Sharks",jamey_eisenberg="CBS's Jamey Eisenberg", dave_richard="CBS's Dave Richard",espn="ESPN",pp="Picking Pros",yahoo="Yahoo Sports",fx="Fox Sports",fft="Fantasy Football Today")
wpremium

htests[,std_upside:=std_pm_h-std_pm]
htests[,std_downside:=std_pm-std_pm_l]

std_big_upsides<-htests[order(-std_upside)][1:5][order(std_ave_rank)][,unique(name)]
std_small_downsides<-htests[order(std_downside)][1:5][order(std_ave_rank)][,unique(name)]

p_and<- function(x) {
  paste(paste(x[1:(length(x)-1)],collapse=", "), "and", x[length(x)])
}

```

The graph below summarises the projections from a variety of sources.  This week's summary includes projections from: `r paste(writers[ffa[,unique(writer)]],collapse=", ")`.

## Standard Scoring Leagues

### Week `r next_week` Wide Recievers 

From this graph be sure to notice:

 - `r p_and(htests[order(-std_upside)][1:5][order(std_ave_rank)][,unique(name)])` have particularly high upsides.  For these players, some projections are placing much higher valuations than others.  If you need to introduce some uncertainty into your game plan, these may be the players to consider.
 - `r p_and(htests[order(std_downside)][1:5][order(std_ave_rank)][,unique(name)])` have little downside to them, which suggests that while their median projection might not be great, there is less uncertainty concerning how poorly they may perform.
 - On the other hand, `r p_and(htests[order(-std_downside)][1:8][order(std_ave_rank)][,unique(name)])` have relatively large downsides this week.  If you are planning on starting them, it may be prudent to investigate.
 
<center> 
```{r,echo=FALSE,fig.height=8,fig.width=8}
#graphing
#geom_point(size=3)+
ggplot(htests, aes(x=std_pm, y=std_rank, color=factor(std_tier))) +
  geom_errorbarh(aes(xmin=std_pm_l,xmax=std_pm_h),height=.3)+
  geom_point(size=5,color="white")+
  geom_text(aes(x=std_pm,label=round(std_pm,0)),size=3)+
  geom_text(aes(x=std_pm_h, label=name, hjust=-0.2, angle=(0), size=1))+
  theme(
    plot.background = element_blank()
    ,panel.grid.major.x = element_line(color="grey")
    ,panel.grid.minor.y = element_line(color="grey")
    ,panel.border=element_rect(color="grey",fill=NA)
    ,panel.background = element_blank()
    ,legend.position = "none"
  ) + scale_y_reverse()+
  ylab("Average Rank") + xlab("Median FPTS Projection with Confidence Interval") +
  labs(title = paste("Week ", next_week, " Wide Reciever Projections", sep="")) +
  coord_cartesian(xlim =c(0,(max(htests$std_pm_h)+10))) 
```
</center>

## Top Recievers - Standard Scoring leagues

```{r,echo=FALSE, results='asis', message=FALSE,warning=FALSE}
kable(ffa[order(std_ave_rank)][,c(sstat(std_fpts),list("Average Rank"=mean(ppr_rank))),
          by=name][1:30])
```


## PPR Leagues

```{r,echo=FALSE,fig.height=10}
#graphing
#geom_point(size=3)+
ggplot(htests, aes(x=ppr_pm, y=ppr_rank, color=factor(ppr_tier))) +
  geom_errorbarh(aes(xmin=ppr_pm_l,xmax=ppr_pm_h),height=.3)+
  geom_point(size=5,color="white")+
  geom_text(aes(x=ppr_pm,label=round(ppr_pm,0)),size=3)+
  geom_text(aes(x=ppr_pm_h, label=name, hjust=-0.2, angle=(0), size=1))+
  theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.grid.minor = element_blank()
    ,panel.border = element_blank()
    ,panel.background = element_blank()
    ,legend.position = "none"
  ) + scale_y_reverse()+
  ylab("Average Rank") + xlab("Average FPTS Projection") +
  labs(title = paste("Week ", next_week, " WRs Uncertainty", sep="")) +
  coord_cartesian(xlim =c(0,(max(htests$ppr_pm_h)+10))) 

```


## Top Recievers - PPR leagues
```{r,echo=FALSE, results='asis'}
kable(ffa[order(ppr_ave_rank)][,c(sstat(ppr_fpts),list("Average Rank"=mean(ppr_rank))),
          by=name][1:30])
```


